### 2020-10-07 doc/manuscript/Dow_manuscript.Rmd
Done first pass of figures 2 and 3

**Figure 1** 
```{r fig1, out.width="100%", echo=FALSE, fig.align="center", fig.cap= "Logistic growth model"}
# Created in RScripts/additional_figures.R
knitr::include_graphics("tables_figures/fig1.png")
```

>>>>

**Figure 1**

Based on D'Orangeville Figure 1

```{r fig1, out.width="100%", echo=FALSE, fig.align="center", fig.cap= "Logistic growth model"}
# Created in RScripts/additional_figures.R
knitr::include_graphics("tables_figures/fig1.png")
```

**Figure 2**

Based on D'Orangeville Figure 3.a), but with relative growth

```{r fig2, out.width="100%", echo=FALSE, fig.align="center", fig.cap= "Percent total (modeled) growth"}
# Created in RScripts/additional_figures.R
knitr::include_graphics("tables_figures/fig2.png")
```

**Figure 3**

Similar to D'Orangeville Figure 4.a), but with cummalative relative growth

```{r fig3, out.width="100%", echo=FALSE, fig.align="center", fig.cap= "Cummulative percent total (modeled) growth"}
# Created in RScripts/additional_figures.R
knitr::include_graphics("tables_figures/fig3.png")
```

**Figure 4**

**Figure 5**
